### 2025-08-26 sandwich_theorem/response_tothe_reviewer.tex

\documentclass[a4paper,twoside,12pt]{article}
\linespread{1}                     % For line spacing
\usepackage{amssymb}                 % For AMS symbol
\usepackage{amsmath,amsthm,latexsym}                 % This is useful for the matrix $\begin{bmatrix} a & b\\ 0 & c\end{bmatrix}$
\usepackage{verbatim}                % For comments in paragraph
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsfig}              % For imbeding graph
\usepackage{color}                  % Color for the text
\usepackage[normal]{caption2}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\setlength{\columnsep}{0.8cm}
\usepackage{makeidx}
\usepackage[normal]{subfigure}
\usepackage{url}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{plain}
%%%%%%%%%%%%%
\textheight23cm%25.0cm
\textwidth16.3cm
\oddsidemargin-0.1cm
\evensidemargin0.1cm
%\topmargin-1cm
\headsep.3cm
%\usepackage{pstricks}

\title{\bfseries A Variant of the Sandwich theorem for two-sided limits}

%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\begin{document}
\begin{center}
{\large  \bfseries Response to the Reviewer Comments on our manuscript The Extension of the Sandwich theorem for two-sided limits}
\end{center}
\vspace{5mm}
\begin{enumerate}
\item \textbf{Response on the comment titled ``Assessment of Novelty'' } \\[2mm]
  The reviewer has pointed out that the result is correct and reviewer has asked for the clarification on our claim that it is a ``Thakuri's Extension''. Here is our clarification:
  \begin{itemize}
  \item
    This is clarified on our revised manuscript submitted. While our theorem follows from the existing variants, our theorem has the novelty enough to call it an extension, because no such relaxation theorem exists for the Sandwich theorem for two-sided limits. \textbf{This has been acknowledge by the five reviewers of Asian Research Journal of Mathematics as well}, whose review details I can send if required. The reviewer has argued that this is not fundamentally new, the same reason we are using the word ``extension'' which means not entirely new but the criterion for the is relaxed.
        \vspace{5mm}

@@

 \item We have revised our claim that to evaluate \(\displaystyle \lim_{x \to 0} \frac{sinx}{x}\) requires our theorem. This can be evaluated without the use of any Sandwich theorem also. We meant to say this cannot evaluated with the bounds we gave.
    \end{itemize}

\vspace{2mm}
\item \textbf{Response on the comment titled ``Key Observations'' } \\[2mm]
  The reviewer has pointed out that even though many textbooks do not include the one-sided version of the Sandwich theorem, the one-sided version aligns with the two sided version. \\[3mm]
  \begin{itemize}
  \item In this revised manuscript we have made the distinction that while our uses one-sided limits ours' is not one-sided version, ours' is two sided version that has incorporated the one-sided limits to relax the criterion.
    \vspace{5mm}
    \item The existing versions that has one-sided limits aligns with the classical Sandwich theorem, because they are the analogous theorem for the one-sided limit. But ours' isn't for the one-sided limits.
  \end{itemize}

\item \textbf{Response on the comment titled ``Key Observations'' } \\[2mm]
  \begin{itemize}
  \item We tried to rephrase the claim to ``variant'' but still we claim that the phrase ``extension'' suits better we our revised manuscript
    \vspace{5mm}

@@

  \item The example $\frac{sinx}{x}$ has acknowledge the better bounds and its solution form the perspective our theorem.

    \vspace{5mm}
  \item We have cited, made reference and given credit to earler versions that led to our theorem. And we have given justification enough to call it an extension.
    \vspace{7mm}
 \item \textcolor{blue}{With the reviewers' insights} we were able to pose a question whether there exists a problem that can be solved cannot be solved by the existing versions of the Sandwich theorem but can be solved by our extension theorem.

 \vspace{7mm}
\item We have added all the references necessary, all the references that led to our work. With the reviewers suggestions we got a direction to dive into earlier works and contributions in this field. We got a chance to refine our article. The excuse for including only one reference is that we came up with this result with the help of that book only. We have given justice to this shortcoming in our revised manuscript. Thank you for the valuable review and the recommendations.

 \vspace{7mm}
\item Still if it feels like we have not justified to call our theorem \textbf{an extension} or if it feels more suitable to call it a \textbf{variant}, then we will send a final article with that change made immediately.
\end{itemize}

 \vspace{9mm}

  \begin{center}
    \LARGE Thank you.
  \end{center}
\end{enumerate}

### 2025-08-26 lecturenotes_aima203/ch1_aima203.tex
advance calculus

\begin{document}
\chapter*{Mathematical Preliminaries}
In this chapter we state, without proof, certain mathematical results which would be useful in the sequel.

\begin{theorem}[\textbf{Rolle's Theorem}]
  If \(f(x)\) is continuous in \([a,b]\), \(f'(x)\) exists in \((a,b)\) and \(f(a)=f(b)=0\), then, there exists at least one number \(c \in (a,b)\) such that \(f'(c)=0\).
\end{theorem}

\begin{theorem}[\textbf{Intermediate value theorem}]
  Let \(f(x)\) be continuous in \([a,b]\) and let \(k\) be any number between \(f(a)\) and \(f(b)\). Then there exists a number \(c \in (a,b)\) such that\(f(c)=k\).
\end{theorem}

\chapter{Errors in Numerical Computing}

>>>>

\begin{document}
\chapter{Errors in Numerical Computing}

### 2025-08-26 lecturenotes_aima203/ch2_aima203.tex
advance calculus

\subsection{Newton-Raphson Method}
Let $(x_0,y_0$ be an initial approximation to the root of the system of equations in two variables~\ref{system}. If $(x_0+h, y_0+k$ is the root of the system, then we must have
\begin{equation*}
  f(x_0+h,y_0+k) = 0 \hspace{1cm} g(x_0+h,y_0+k) = 0
\end{equation*}
Assuming that $f$ and $g$ are sufficiently differentiable, we expand both of these functions by Taylor's series to obtain
\begin{equation*}
  \begin{gathered}[t]
    f_0 +h\frac{\partial f}{\partial x_0} + k\frac{\partial f}{\partial y_0}... = 0 \\
    g_0 +h\frac{\partial g}{\partial x_0} + k\frac{\partial g}{\partial y_0}... = 0
  \end{gathered}
\end{equation*}
where, \hspace{5mm} $\displaystyle \frac{\partial f}{\partial x_0} = \left [\frac{\partial f}{\partial x} \right ] _{x=x_0}$, $f_0 = f(x_0,y_0)$, etc \\[1mm]
Neglating the second and higher-order derivatives terms, we get,
\begin{equation}
  \label{taylor}
  \begin{gathered}[b]
    h\frac{\partial f}{\partial x_0} + k\frac{\partial f}{\partial y_0}... = -f_0 \\
     h\frac{\partial g}{\partial x_0} + k\frac{\partial g}{\partial y_0}... = g_0
  \end{gathered}
\end{equation}
The system of equations~\ref{taylor} possesses a unique solution if
$$ D =
\left \vert \begin{matrix}
  \frac{\partial f}{\partial x_0}  & \frac{\partial f}{\partial y_0} \\[2mm]
  \frac{\partial g}{\partial x_0}  & \frac{\partial g}{\partial y_0}
\end{matrix} \right \vert  \neq 0
$$
By Cramer's rule
\begin{equation}
  h= \frac{1}{D}\, \left \vert \begin{matrix}
  -f_0  & \frac{\partial f}{\partial y_0} \\[2mm]
  -g_0  & \frac{\partial g}{\partial y_0}
\end{matrix} \right \vert \hspace{5mm} and \hspace{5mm} k= \frac{1}{D}\, \left \vert \begin{matrix}
  \frac{\partial f}{\partial y_0} & -f_0  \\[2mm]
 \frac{\partial g}{\partial y_0} &  -g_0
\end{matrix} \right \vert
\end{equation}
The new approximations are, therefore
\begin{equation}
  x_1 = x_0 +h \hspace{5mm} and \hspace{5mm} y_1 = y_0 + k
\end{equation}
\begin{figure}[h]
  \centering
\includegraphics[width=15cm, height=7cm]{newton_example.png}
\end{figure}

>>>>

\subsection{Newton-Raphson Method}
Let $(x_0,y_0)$ be an initial approximation to the root of the system of equations in two variables~\ref{system}. If $(x_0+h, y_0+k)$ is the root of the system, then we must have
\begin{equation*}
  f(x_0+h,y_0+k) = 0 \hspace{1cm} g(x_0+h,y_0+k) = 0
\end{equation*}
Assuming that $f$ and $g$ are sufficiently differentiable, we expand both of these functions by Taylor's series to obtain
\begin{equation*}
  \begin{gathered}[t]
    f_0 +h\frac{\partial f}{\partial x_0} + k\frac{\partial f}{\partial y_0}... = 0 \\
    g_0 +h\frac{\partial g}{\partial x_0} + k\frac{\partial g}{\partial y_0}... = 0
  \end{gathered}
\end{equation*}
where, \hspace{5mm} $\displaystyle \frac{\partial f}{\partial x_0} = \left [\frac{\partial f}{\partial x} \right ] _{x=x_0}$, $f_0 = f(x_0,y_0)$, etc \\[1mm]
Neglating the second and higher-order derivatives terms, we get,
\begin{equation}
  \label{taylor}
  \begin{gathered}[b]
    h\frac{\partial f}{\partial x_0} + k\frac{\partial f}{\partial y_0}... = -f_0 \\
     h\frac{\partial g}{\partial x_0} + k\frac{\partial g}{\partial y_0}... = -g_0
  \end{gathered}
\end{equation}
The system of equations~\ref{taylor} possesses a unique solution if
$$ D =
\left \vert \begin{matrix}
  \frac{\partial f}{\partial x_0}  & \frac{\partial f}{\partial y_0} \\[2mm]
  \frac{\partial g}{\partial x_0}  & \frac{\partial g}{\partial y_0}
\end{matrix} \right \vert  \neq 0
$$
By Cramer's rule
\begin{equation}
  h= \frac{1}{D}\, \left \vert \begin{matrix}
  -f_0  & \frac{\partial f}{\partial y_0} \\[2mm]
  -g_0  & \frac{\partial g}{\partial y_0}
\end{matrix} \right \vert \hspace{5mm} and \hspace{5mm} k= \frac{1}{D}\, \left \vert \begin{matrix}
  \frac{\partial f}{\partial x_0} & -f_0  \\[2mm]
 \frac{\partial g}{\partial x_0} &  -g_0
\end{matrix} \right \vert
\end{equation}
The new approximations are, therefore
\begin{equation}
  x_1 = x_0 +h \hspace{5mm} and \hspace{5mm} y_1 = y_0 + k
\end{equation}
\begin{figure}[h]
  \centering
\includegraphics[width=15cm, height=7cm]{newton_example.png}
\end{figure}

### 2025-08-26 lecturenotes_aima203/ch7_aima203.tex
advance calculus

    \columnbreak
    b). $\displaystyle y''(x) \approx \frac{y(x+h) - 2y(x)+ y(x-h)}{h^2}$
  \end{multicols}
\end{enumerate}
These formulae can be easily derived by expanding $y(x)$ in the neighborhood of $x$ using Taylor's series. In general for higher order derivatives central difference formula gives better accuracy so,this formula is commonly used.

@@

\begin{example}
  Solve: $y'' - cosx\, y' -sinx \, y = e^x, \hspace{10mm} y(0)=0, \hspace{3mm} y(1)=1$ \\
  \textbf{Solution Steps:}
  \begin{enumerate}
  \item   Here, $x_0 = 0$ and $x_n = 1$. Choosing $n=4$ we get $h = (1-0)/4 = 0.25$.

  \item At $x=x_i$ we have $\displaystyle \frac{y_{i+1} - 2y_i+ y_{i-1}}{h^2} -cosx_i \; \frac{y_{i+1} - y_{i-1}}{2h} - sinx_i \; y_i = e^{x_i}$ \\[1mm]
    Substituting $h=0.25$, we  get, $\displaystyle \frac{y_{i+1} - 2y_i+ y_{i-1}}{(0.25)^2} -cosx_i \; \frac{y_{i+1} - y_{i-1}}{2(0.25)} - sinx_i \; y_i = e^{x_i}$

\item Simplifying: $(16+2cosx_i)y_{i-1} + (sinx_i-32)y_i + (16 -2cosx_i)y_{i+1} = e^{x_i}$

\item Substituting $x_0=0, \;\;\; x_1=0.25, \;\;\; x_2=0.5, \;\;\; x_3= 0.75$ and $y_0=1, \;\;\; y_4=1$:
  \begin{align*}
    (16+2cos(0.25))0 + (sin(0.25)-32)y_1 + (16 -2cos(0.25))y_2 &= e^{0.25} \\[1mm]
    (16+2cos(0.5))y_1 + (sin(0.5)-32)y_2 + (16 -2cos(0.5))y_3 &= e^{0.5} \\[1mm]
    (16+2cos(0.75))y_2 + (sin(0.75)-32)y_3 + (16 -2cos(0.75))1 &= e^{0.75}
  \end{align*}

\item Simplifying:
  \begin{equation}
    \label{examplesystem}
  \begin{aligned}[c]
    -32.24\, y_1 + 14.06 \, y_2 &= 1.28 \\[1mm]
    17.75 \, y_1 - 32.48\, y_2 14.24 \, y_3 &= 1.64 \\[1mm]
    17.46 \, y_2  -32.68\, y_3 + 14.54 &= 2.11
  \end{aligned}
\end{equation}

\item Solving: $y_1 = 0.01, \;\;\; y_2=0.38, \;\;\; y_3=0.98$.
  \end{enumerate}

>>>>

    \columnbreak
    b). $\displaystyle y''(x) \approx \frac{y(x+h) - 2y(x)+ y(x-h)}{h^2}$
  \end{multicols}
\end{enumerate}
\begin{mdframed}
  In principle the central difference formula should be $\displaystyle y'(x) \approx \frac{y(x+h/2) - y(x-h/2)}{h}$ but for easier computation during program execution the above formula has been adopted.
\end{mdframed}
These formulae can be easily derived by expanding $y(x)$ in the neighborhood of $x$ using Taylor's series. In general for higher order derivatives central difference formula gives better accuracy so,this formula is commonly used.

@@

\begin{example}
  Solve: $y'' - cosx\, y' -sinx \, y = e^x, \hspace{10mm} y(0)=0, \hspace{3mm} y(1)=1$, taking $n=4$.\\
  \textbf{Solution Steps:}
  \begin{enumerate}
  \item   Here, $x_0 = 0$ and $x_n = 1$. Choosing $n=4$ we get $h = (1-0)/4 = 0.25$.

  \item At $x=x_i$ we have $\displaystyle \frac{y_{i+1} - 2y_i+ y_{i-1}}{h^2} -cosx_i \; \frac{y_{i+1} - y_i}{h} - sinx_i \; y_i = e^{x_i}$ \\[1mm]
    Substituting $h=0.25$, we  get, $\displaystyle \frac{y_{i+1} - 2y_i+ y_{i-1}}{(0.25)^2} -cosx_i \; \frac{y_{i+1} - y_i}{0.25} - sinx_i \; y_i = e^{x_i}$

\item Simplifying: $16y_{i-1} + (-32+4cosx_i-sinx_i)y_i + (16 -4cosx_i)y_{i+1} = e^{x_i}$

\item Substituting $x_0=0, \;\;\; x_1=0.25, \;\;\; x_2=0.5, \;\;\; x_3= 0.75$ and $y_0=1, \;\;\; y_4=1$:
  \begin{align*}
    (16)0 + (-32+4cos(0.25)-sin(0.25)) (16 -4cos(0.25))y_2 &= e^{0.25} \\[1mm]
    16y_1 + (-32+4cos(0.5)-sin(0.5))y_2 + (16 -4cos(0.5))y_3 &= e^{0.5} \\[1mm]
    16y_2 + (-32+4cos(0.75)-sin(0.75))y_3 + (16 -4cos(0.75))1 &= e^{0.75}
  \end{align*}

\item Simplifying:
  \begin{equation}
    \label{examplesystem}
  \begin{aligned}[c]
    -28.371\, y_1 + 12.124 \, y_2 &= 1.284 \\[1mm]
    16 \, y_1 - 28.969\, y_2 +12.489 \, y_3 &= 1.648 \\[1mm]
    16 \, y_2  -29.754\, y_3 + 14.54 &= -10.956
  \end{aligned}
\end{equation}

\item Solving: $y_1 = 0.016, \;\;\; y_2=0.144, \;\;\; y_3=0.445$.
\end{enumerate}
\begin{table}[h]
  \centering
  \begin{tabular}{|c|c|}
    \hline
    x&y \\
    \hline
    0 & 0 \\
    0.25 & 0.016 \\
    0.5 & 0.144 \\
    0.75 & 0.454 \\
    1 & 1 \\
    \hline
  \end{tabular}
\end{table}

### 2025-08-26 lecturenotes_aima331/ch3_aima331.tex
advance calculus

\message{ !name(ch3_aima331.tex)}\documentclass[aima331_lecturenotes_ku.tex]{subfiles}
\setcounter{chapter}{2}
\begin{document}

\message{ !name(ch3_aima331.tex) !offset(-3) }

\chapter{Fourier Transform}
\section{Fourier Integral}
Fourier series are powerful tools for problems involving functions that are periodic or are of interest on a finite interval only. The idea of Fourier series extended to the functions that are nonperiodic gives Fourier Integral. The Fourier Integral Representation of a function $f(x)$ is
\begin{equation}
   \label{fourier_integral}
  \begin{gathered}[t]
    f(x) = \int_0^{\infty} \; \left [ A(w)\, cos\,wx + B(w)\, sin\,wx \right] \\[2mm]
     \text{where,} \hspace{2mm} A(w) =\frac{1}{\pi} \int_{-\infty}^{\infty} \; f(v)\,cos\,wv\,dv, \hspace{7mm} B(w) =\frac{1}{\pi} \int_{-\infty}^{\infty} \; f(v)\,sin\,wv\,dv
    \end{gathered}
  \end{equation}

@@

 \subsubsection{Procedure}
 \begin{enumerate}
 \item Take Fourier transform with respect to the variable $x$ on the both sides of the PDE~\ref{heat}.
   Let, $\displaystyle U(w,t) = \frac{1}{\sqrt{2\pi}} \; \int_{-\infty}^{\infty} \; u(x,t)\, e^{-iwx}\,dx$. Then, \\[3mm]
   $\displaystyle U_t(w,t) = \frac{1}{\sqrt{2\pi}} \; \int_{-\infty}^{\infty} \; u_t(x,t)\, e^{-iwx}\,dx = \frac{1}{\sqrt{2\pi}} \; \int_{-\infty}^{\infty} \;k\, u_{xx}(x,t)\, e^{-iwx}\,dx$. \\[2mm]
   Now from the derivative of Fourier transform, $\mathcal{F}(f^{''})(w)=(iw)^2\mathcal{F}_c(f)(w)=-w^2\mathcal{F}_c(f)(w)$, we have, so,
   \begin{equation}
     \label{eq:2}
     \begin{aligned}
       U_t(w,t) &= k \mathcal{F}(u_{xx})(w,t) = -kw^2U(w,t) \\[2mm]
       U_t(w,t) + kw^2U(w,t) =0
     \end{aligned}
   \end{equation}

@@

\message{ !name(ch3_aima331.tex) !offset(-255) }

>>>>

\documentclass[aima331_lecturenotes_ku.tex]{subfiles}
\setcounter{chapter}{2}
\begin{document}
\chapter{Fourier Transform}
\section{Fourier Integral}
Fourier series are powerful tools for problems involving functions that are periodic or are of interest on a finite interval only. The idea of Fourier series extended to the functions that are nonperiodic gives Fourier Integral. The Fourier Integral Representation of a function $f(x)$ is
\begin{equation}
   \label{fourier_integral}
  \begin{gathered}[t]
    f(x) = \int_0^{\infty} \; \left [ A(w)\, cos\,wx + B(w)\, sin\,wx \right] \\[2mm]
     \text{where,} \hspace{2mm} A(w) =\frac{1}{\pi} \int_{-\infty}^{\infty} \; f(v)\,cos\,wv\,dv, \hspace{7mm} B(w) =\frac{1}{\pi} \int_{-\infty}^{\infty} \; f(v)\,sin\,wv\,dv
    \end{gathered}
  \end{equation}

@@

 \subsubsection{Procedure}
 \begin{enumerate}
 \item Take Fourier transform with respect to the variable $x$ on the both sides of the PDE~\ref{heat}.
   Let, $\displaystyle U(w,t) = \frac{1}{\sqrt{2\pi}} \; \int_{-\infty}^{\infty} \; u(x,t)\, e^{-iwx}\,dx$. Then, \\[3mm]
   $\displaystyle U_t(w,t) = \frac{1}{\sqrt{2\pi}} \; \int_{-\infty}^{\infty} \; u_t(x,t)\, e^{-iwx}\,dx = \frac{1}{\sqrt{2\pi}} \; \int_{-\infty}^{\infty} \;k\, u_{xx}(x,t)\, e^{-iwx}\,dx$. \\[2mm]
   Now from the derivative of Fourier transform, $\mathcal{F}(f^{''})(w)=(iw)^2\mathcal{F}_c(f)(w)=-w^2\mathcal{F}_c(f)(w)$, we have, so,
   \begin{equation}
     \label{heat_ordinary}
     \begin{aligned}[b]
       U_t(w,t) &= k \mathcal{F}(u_{xx})(w,t) = -kw^2U(w,t) \\[2mm]
       U_t(w,t) + kw^2U(w,t) &=0 \\[2mm]
       U_t + kw^2U &=0
     \end{aligned}
   \end{equation}

 \item The transformed equation~\ref{heat_ordinary} is an ordinary differential equation of order one and degree one. The general solution whose is $$ U(w,t) = A(w) \,e^{-kw^2t} $$,
   where $A(w)$ is a totally arbitary function of $w$. The determination of the $A(w)$ gives the partial solution.

 \item Using the above initial condition,
   $$A(w)=U(w,0)=\frac{1}{\sqrt{2\pi}} \; \int_{-\infty}^{\infty} \; u(x,0)\, e^{-iwx}\,dx= \frac{1}{\sqrt{2\pi}} \; \int_{-\infty}^{\infty} \; f(x)\, e^{-iwx}\,dx = \hat{f}(w)$$

 \item Thus, $U(w,t) = \hat{f}(w)\, e^{-kw^2t}$ is the solution of the transformed equation. Now we take inverse Fourier transform on both sides to get $u$ which is the solution of the original PDE.
   $$u = \mathcal{F}^{-1}\,(\hat{f}(w)\, e^{-kw^2t})$$

@@

### 2025-08-26 question_papers/aima104_mcq_second_in_sem.tex
advance calculus

\begin{center}
  {\bfseries  {\large Kathmandu University}} \\
  First In-semester Examination-2025 \\[-2mm]
    \textbf{\small Department of Artificial Intelligence, Panchkhal}
\end{center}
\vspace{2mm}

@@

\begin{center}
  SECTION''A'' \hspace{5mm} [10 Q \(\times\) 1 = 10 marks] (\textbf{\textit{Do any ten}}).
\end{center}
Fill in the blanks by writing the most appropriate word(s) or symbol(s).
\begin{questions}
\question Give an example of a vector and its scalar. \rule{7cm}{0.15mm}.
\question Give an example of a subspace of $\mathbb{R}^2$ : \rule{8cm}{0.15mm}.

\question Give an example of $3 \times 4 $ row echelon for matrix. \rule{7cm}{0.15mm}.

\question Find the rank of the matrix $\displaystyle \begin{bmatrix}
    1 & 3 & 5 \\
    2 & 6 & 10 \\
    4  & 12 & 20
\end{bmatrix}.$ \rule{7cm}{0.15mm}.

\question Determine whether the system has unique solution, no unique solution or no solution. $ \left[ \begin{matrix}
    1 & 0  \\
    0 & 1  \\
    0 & 0
\end{matrix} \;\; \vline \;\;
\begin{matrix}
    0\\ 0\\ -1
\end{matrix} \right]$ \rule{7cm}{0.15mm}.

\question Write a basis of the vector space $\{0\}$. \rule{7cm}{0.15mm}.

\question Suppose a $4 \times 7$ matrix $A$ has four pivot columns. Is $Col(A) = \mathbb{R}^4$? Is $Nul(A) = \mathbb{R}^3$ ? \rule{12cm}{0.15mm}.

\question Is the set of vectors linearly dependent?$\{(1,2, 4) \;\; (2,4,8)\}$ \rule{4cm}{0.15mm}.

\question What are the eigenvalues of a triangular matrix? \rule{7cm}{0.15mm}.

\question Explain why there are infinitely many eigenvalues associated with an eigenvalue.\\[1mm]
  \rule{12cm}{0.15mm}.

\question If $Ax=2x$ then, $AAx=?$ \rule{7cm}{0.15mm}.

\question Can you explain the case where zero is an eigenvalue of a matrix? \\[1mm] \rule{12cm}{0.15mm}.
\end{questions}

>>>>

\begin{center}
  {\bfseries  {\large Kathmandu University}} \\
  Second In-semester Examination-2025 \\[-2mm]
    \textbf{\small Department of Artificial Intelligence}
\end{center}
\vspace{2mm}

@@

\begin{center}
  SECTION''A'' \hspace{5mm} [10 Q \(\times\) 1 = 10 marks] (\textbf{\textit{Do any ten}}).
\end{center}
Fill in the blanks by writing the most appropriate word(s) or symbol(s).
\begin{questions}
\question Is $
  \begin{bmatrix}
    1 \\ 4
  \end{bmatrix}$ an eigenvector of $\begin{bmatrix} -3 & 1  \\  -3 & -8  \\ \end{bmatrix}$ ? \rule{7cm}{0.15mm}.
\question Give an example of a subspace of $\mathbb{R}^2$ : \rule{8cm}{0.15mm}.

\question What is the sufficient condition for diagonalization of a matrix? \rule{4cm}{0.15mm} \\[1mm]
\rule{9cm}{0.15mm}.

\question Write the relationship between algebraic multiplicity and geometric multiplicity of an eigenvalue. \rule{8cm}{0.15mm}.

\question Compute the distance between: $u=
  \begin{bmatrix}
    -1 \\ 2
  \end{bmatrix}, \vspace{4mm}
   v=
   \begin{bmatrix}
     4 \\6
   \end{bmatrix}$ \rule{7cm}{0.15mm}.

\question Find the angle between $u$ and $v$ given above. \rule{7cm}{0.15mm}.

\question Let $W$ be a subspace of $V$. What is the intersection between $W$ and $W^{\perp}$? \rule{3cm}{0.15mm}.

\question In QR factorization, what is the nature of $R$? \rule{7cm}{0.15mm}.
\vspace{2mm}

\question Give an example of Hermitian matrix. \rule{7cm}{0.15mm}.

\question Find orthogonal projection of $u$ onto $v$ for the given $u$ and $v$ in question 5. \rule{3cm}{0.15mm}. \\[1mm]
\rule{7cm}{0.15mm}.
\end{questions}

### 2025-08-26 question_papers/aima203_mcq_second_in_sem.tex
advance calculus

\begin{center}
  SECTION''A'' \hspace{5mm} [10 Q \(\times\) 1 = 10 marks] (\textit{Do any ten}).
\end{center}
Fill in the blanks by writing the most appropriate word(s) or symbol(s).
\begin{questions}

\question Write the number of significant digits in 20300.00  \rule{5cm}{0.15mm}.
  \vspace{2mm}

  \question Write the precision and accuracy of 45.2030  \rule{5cm}{0.15mm}.

  \question Find the upper limit error in rounding a number to $4$ decimal places.\rule{4cm}{0.15mm}.

    \question What is the maximum number of positive real roots of $x^5-x^4+3x^3-x^2-x+2$? \rule{7cm}{0.15mm}.

    \question Which error: Truncation error or rounding off error in Newton Raphson's method? \rule{5cm}{0.15mm}.

    \question Which one converges faster bisection method or secant method? \rule{5cm}{0.15mm}.

    \question Write the disadvantage of ``Lagrange's Interpolation method'': \rule{5cm}{0.15mm} \\[1mm]
      \rule{10cm}{0.15mm}.

    \question Write the advantage of ``Secant method over Newton Rapshon's method'': \\[1mm]
      \rule{12cm}{0.15mm}.

    \question Write the formula for $\Delta y_1$ and $\nabla y_1$: \rule{7cm}{0.15mm}.

    \question What is the difference of interpolation and extrapolation. \rule{5cm}{0.15mm} \\[1mm]
      \rule{12cm}{0.15mm}.

 \question Calculate the number of steps taken by Bisection method to get the accuracy less than $10^{-3}$.\rule{8cm}{0.15mm}.
\end{questions}

>>>>

\begin{center}
  SECTION''A'' \hspace{5mm} [10 Q \(\times\) 1 = 10 marks] (\textit{Do any ten}).
\end{center}
Fill in the blanks by writing the most appropriate word(s) or symbol(s).
\begin{questions}
  \question Write the condition for the natural quadratic spline. \rule{7cm}{0.15mm}.
\vspace{2mm}
  \question Write the condition for the natural cubic spline. \rule{7cm}{0.15mm}.
\vspace{2mm}
  \question Write a major drawback of linear splines. \rule{7cm}{0.15mm}.
\vspace{2mm}
  \question Why is cubic spline the most popular one? \rule{7cm}{0.15mm} \\[1mm]
  \rule{9cm}{0.15mm}.
\vspace{2mm}
  \question What are $m_i$'s and $M_i$'s in the quadratic and cubic splines? \rule{5cm}{0.15mm}.
\vspace{2mm}
  \question Write the formula for Romberg's Integration using Trapezoidal rule. \rule{4cm}{0.15mm}.
\vspace{2mm}
  \question From where the $u_i$'s are obtained in Gaussian quadrature. \rule{5cm}{0.15mm}.
\vspace{2mm}
  \question Write an second-degree IVP. \rule{9cm}{0.15mm}.
\vspace{2mm}
\question Write an second-degree BVP. \rule{9cm}{0.15mm}.
\vspace{2mm}
  \question Difference between forward Euler method and backward Euler method: \rule{2cm}{0.15mm} \\[1mm]
    \rule{9cm}{0.15mm}.

\end{questions}
